Comparison to other studies

### 2024-11-14 pages/other_studies.qmd
docs(discussion): add some more studies

@@

>>>>

| @stodden_empirical_2018 | Articles from Science before and after policy change around code sharing | 22 | After policy was 204 articles - could identify artefacts themselves for 24, but contacted authors for 180, of which 131 replied - of which got data/code for 65/180 (36\%). From looking at the then total of 89 article artefacts, anticipated 56 to looked potentially reproducible. Chose 22 of them and were able to replicate results in publication for all except one (large dataset and software no longer acccesible). Issues in those thought not to reproduce were missing scripts, documentation, or parameters. Few papers cited visualisation tools, even when visualisation in article were important. |

@@

Examples that just try and run code but don't check results:

* @trisovic_large-scale_2022 - R code from the Harvard Dataverse repository | 9000 unique R files from 2000+ replication packages - with interesting oobservations about basic code cleaning, whether there's documentation and comments, and some stuff about **backwards compatability of R** and how it does become non-compatabile
